Legacy Data Confounds Genomics Studies

### 2019-03-05 legacy.tex
updated Han Resequenced plots

We did a similar analysis using the variants identified in the \textit{5PC} model present in the 83 resequenced individuals.
Of the 11,416 suspicious variants identified globally, only 8,697 of them are found in the 83 individuals in the original 1kGP data.
From this subset, 8,085 of these variants are missing entirely from the resequenced data.
We noticed a unusually large number of INDELs that are fixed in the resequenced data that are at lower frequencies in the 1kGP. (See Figure \ref{90HanSFS_full})

@@

We found that 476 of the variants we identified as being associated to $Q$ were present on Illumina's Omni 2.5 chip. This does not mean that these variants are false positives, but rather, that in the 1kGP, individuals with low $Q$ were less likely to be called as having a variant in that position. Moreover, using the 1kGP as a reference panel might impact the population allele frequencies observed for these positions.

>>>>

We did a similar analysis using the variants identified in the \textit{5PC} model present in the 83 resequenced individuals.
Of the 11,416 suspicious variants identified globally, only 7,607 of them are found in the 83 individuals in the original 1kGP data.
From this subset, only 613 of these variants are present in the resequenced data, the rest are missing entirely.
We noticed a unusually large number of INDELs that are fixed in the resequenced data that are at lower frequencies in the 1kGP. (See Figure \ref{90HanSFS_full})

@@

We found that 219 of the variants we identified as being associated to $Q$ were present on Illumina's Omni 2.5 chip. This does not mean that these variants are false positives, but rather, that in the 1kGP, individuals with low $Q$ were less likely to be called as having a variant in that position. Moreover, using the 1kGP as a reference panel might impact the population allele frequencies observed for these positions.
